Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex
hartley entropy for C

\textbf{Notes:}
Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
 Codes where $\log |C| = \Theta(\ell)$ and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.  See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.

@@

\begin{theorem}
\label{thm:main thm first cons}
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_i$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.  Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
\end{theorem}
\begin{proof}
We argue security in~\lemref{lem:security of cons} and correctness in~\lemref{lem:correct of cons}.
\end{proof}

\begin{lemma}
\label{lem:security of cons}
Let all variables be as in \thref{thm:main thm first cons}.  For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{lemma}

We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
\begin{proof}[Outline]
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $J$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{J^c} = C'_{J^c}) = |C| - |J^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\end{proof}
We now a rgue correctness of \consref{cons:first construction}.
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Recall that $c$ contains at most $\ell$ $1$s.  Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/|\mathcal{Z}|$. Since the $r_i$ are chosen independently, one has,
\[
\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{|\mathcal{Z}|}.
\]
\end{proof}

@@

We consider what entropy is necessary for security.  The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
%Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.  %We achieve security when $\Huse\le 0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.

@@

\begin{theorem}
\label{thm:sampling}
Let $n$ be a security parameter.
Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.   Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
$\ell = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
\tilde{m} &=|C|\\
\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
\end{align*}
\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
\end{theorem}

@@

Thus, unless the choice of $\lambda$ is very unlucky,
\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. This allows us to conclude the following.
\begin{corollary}
\label{cor:samp unguess}
Let all the variables be as in \thref{thm:sampling}.
For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
\end{proof}

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in J$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |J|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |J|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

@@

Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.  Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq |C|- \beta$. % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < |C|-\beta$.

By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.  Then $C | C_{J^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{J^c} )= |C| -\beta$ and thus $\Hav(C'| C_{J^c}) = |C| -\beta$.
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two codewords that agree on $J^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
\begin{lemma}
\label{lem:codewords in I close}
Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
\[
\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in J$, $\Hav(W_i | View(S))\geq \alpha$.  The only information about the correct value of $c_i^*$ is contained in the query responses.  When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.  We now show that for any value of $c^*$ all queries on $i \in J$ return $0$ with probability $1-2^{-\alpha+1}$.  Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.  Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.  Thus, it must occur with probability:
\begin{align}
2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
 &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
\end{align}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
\label{cl:ent bounded away from n}
$\alpha \le n-\log q$
\end{claim}
\begin{proof}
It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.  Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
This completes the proof of \clref{cl:ent bounded away from n}.
\end{proof}
\noindent
Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).  By the union bound over the indices $i\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$. Recall that $c^*, c'$ match on all indices outside of $J$. Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.  This concludes the proof of \lemref{lem:codewords in I close}
\end{proof}
By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.  This completes the proof of \lemref{lem:sim cannot distinguish}.
\end{proof}

>>>>

\textbf{Notes:}
Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
 Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.  See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.

@@

\begin{theorem}
\label{thm:main thm first cons}
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_i$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.  Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C)- \beta$.
\end{theorem}
\begin{proof}
We argue security in~\lemref{lem:security of cons} and correctness in~\lemref{lem:correct of cons}.
\end{proof}

\begin{lemma}
\label{lem:security of cons}
Let all variables be as in \thref{thm:main thm first cons}.  For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{lemma}

We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
\begin{proof}[Outline]
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $J$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{J^c} = C'_{J^c}) = H_0(C) - |J^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\end{proof}
We now a rgue correctness of \consref{cons:first construction}.
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Recall that $c$ contains at most $\ell$ $1$s.  Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/|\mathcal{Z}|$. Since the $r_i$ are chosen independently, one has,
\[
\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{|\mathcal{Z}|}.
\]
\end{proof}

@@

We consider what entropy is necessary for security.  The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).
%Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.  %We achieve security when $\Huse\le 0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.

@@

\begin{theorem}
\label{thm:sampling}
Let $n$ be a security parameter.
Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.   Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
$\ell = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
\tilde{m} &=H_0(C)\\
\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
\end{align*}
\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
\end{theorem}

@@

Thus, unless the choice of $\lambda$ is very unlucky,
\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. This allows us to conclude the following.
\begin{corollary}
\label{cor:samp unguess}
Let all the variables be as in \thref{thm:sampling}.
For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq H_0(C)$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
\end{proof}

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in J$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |J|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |J|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

@@

Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.  Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$. % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.

By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.  Then $C | C_{J^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{J^c} )= H_0(C) -\beta$ and thus $\Hav(C'| C_{J^c}) = H_0(C) -\beta$.
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two codewords that agree on $J^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
\begin{lemma}
\label{lem:codewords in I close}
Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
\[
\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in J$, $\Hav(W_i | View(S))\geq \alpha$.  The only information about the correct value of $c_i^*$ is contained in the query responses.  When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.  We now show that for any value of $c^*$ all queries on $i \in J$ return $0$ with probability $1-2^{-\alpha+1}$.  Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.  Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.  Thus, it must occur with probability:
\begin{align}
2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
 &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
\end{align}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
\label{cl:ent bounded away from n}
$\alpha \le n-\log q$
\end{claim}
\begin{proof}
It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.  Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
This completes the proof of \clref{cl:ent bounded away from n}.
\end{proof}
\noindent
Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).  By the union bound over the indices $i\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$. Recall that $c^*, c'$ match on all indices outside of $J$. Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.  This concludes the proof of \lemref{lem:codewords in I close}.
\end{proof}
By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.  This completes the proof of \lemref{lem:sim cannot distinguish}.
\end{proof}
